\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{float}
\usepackage{mathptmx}    % Times New Roman for text and math


% Set section/subsection font size to 14pt/12pt and title to 16pt
\usepackage{sectsty}
\sectionfont{\fontsize{14}{16}\selectfont}
\subsectionfont{\fontsize{12}{14}\selectfont}
\usepackage{titling}
\title{IoT Final Project: ESP32 Fingerprint Attendance System}
\author{Ngo Hoang Nhat Khang \\ Ho Anh Tuan \\ Tran Ngoc Quan \\ Tran Minh Hoang}
\date{\today}
\begin{document}

\maketitle

\section{System Overview}

This project implements a fingerprint-based attendance system using ESP32 microcontrollers connected to a Raspberry Pi 5 server with an admin dashboard. The system allows users to check in and out using biometric authentication.

\subsection{System Architecture}

The system consists of three main components:

\begin{enumerate}
    \item \textbf{ESP32 + Fingerprint Sensor}: Edge devices for biometric authentication
    \item \textbf{Raspberry Pi 5 Server + Database}: Central server for data processing and storage
    \item \textbf{Admin Dashboard}: Web interface for system management
\end{enumerate}

Data flows as follows:
$$\text{Fingerprint} \rightarrow \text{ESP32} \xrightarrow{\text{WiFi}} \text{Raspberry Pi 5 Server} \xrightarrow{\text{Web}} \text{Dashboard}$$

\section{Hardware Components}

\subsection{ESP32 Node}
\begin{itemize}
    \item ESP32 Development Board
    \item Fingerprint Sensor (AS608)
    \item I2c LED for display status 
    \item Buzzer for feedback
    \item 5V Power supply
\end{itemize}

\subsection{Server Setup}
\begin{itemize}
    \item Raspberry Pi 5 (4GB RAM)
    \item 32GB microSD card
    \item Network connection (Ethernet/WiFi)
\end{itemize}

\section{System Features}

\subsection{Core Functionality}
\begin{itemize}
    \item Fingerprint enrollment and verification
    \item Check-in/check-out timestamp recording
    \item Real-time data synchronization
    \item Multi-user support
    \item Attendance report generation
\end{itemize}

\subsection{Operational Flow}
\begin{enumerate}
  \item ESP32 and Raspberry Pi connect to WiFi on startup using configured credentials.
  \item \textbf{Admin Mode (1234\#)}: Enter \texttt{1234\#} on the ESP32 keypad to activate.
  \begin{itemize}
    \item \texttt{1\#}: Add Employee – enter fingerprint ID, place finger, remove, model created and stored.
    \item \texttt{2\#}: Delete Employee.
    \item \texttt{3\#}: Generate Report.
    \item \texttt{4\#}: Reset Sensor.
    \item \texttt{9\#}: Exit Admin Mode.
  \end{itemize}
  \item \textbf{Normal Operation}: Users scan fingerprint for attendance.
  \begin{itemize}
    \item First scan: CHECK-IN OK, then 10\,s delay before checkout allowed.
    \item Second scan: CHECK-OUT OK.
  \end{itemize}
\end{enumerate}

\subsection{Database Schema}
The system uses two main tables:
\begin{itemize}
    \item \textbf{Users Table}: Stores user information and fingerprint IDs
    \item \textbf{Attendance Table}: Records check-in/out events with timestamps
\end{itemize}

\subsection{Communication and Data Storage}
\begin{itemize}
    \item Local database connection using SQLite
    \item MQTT protocol for messaging between ESP32 nodes and the Raspberry Pi server
\end{itemize}

\section{Implementation Process}

\subsection{Hardware Setup}
\begin{enumerate}
    \item Connect fingerprint sensor to ESP32 via UART pins
    \item Install Raspberry Pi OS on RPi5
    \item Configure network connectivity
\end{enumerate}

\subsection{Software Development}
\begin{enumerate}
    \item Program ESP32 firmware for fingerprint handling
    \item Develop server API for data processing
    \item Create web dashboard for administration
    \item Test system integration
\end{enumerate}

\section{Security Features}

\begin{itemize}
    \item Encrypted fingerprint template storage
    \item HTTPS communication
    \item User authentication for dashboard access
    \item Regular data backups
\end{itemize}

\section{Cost Analysis}

\begin{center}
\begin{tabular}{|l|r|}
\hline
\textbf{Component} & \textbf{Cost (USD)} \\
\hline
ESP32 + Fingerprint Sensor & \$25 \\
Raspberry Pi 5 Setup & \$120 \\
Additional Components & \$15 \\
\hline
\textbf{Total System Cost} & \$160 \\
\hline
\end{tabular}
\end{center}

\section{Applications}

This system is suitable for:
\begin{itemize}
    \item Office attendance tracking
    \item School/university attendance
    \item Access control systems
    \item Time and attendance management
\end{itemize}

\section{Conclusion}

The ESP32 fingerprint attendance system provides an affordable and reliable solution for automated attendance tracking. The distributed architecture ensures scalability while the web-based dashboard offers easy management capabilities.

\textbf{Key Benefits:}
\begin{itemize}
    \item Cost-effective implementation
    \item Contactless operation
    \item Real-time data processing
    \item Scalable architecture
    \item User-friendly interface
\end{itemize}

% [MORE INFO NEEDED: Specific implementation details for your school's requirements]
% [MORE INFO NEEDED: Testing results and performance measurements]
\section*{Source Code}
The full source code for this project is available on GitHub: \url{https://github.com/khang-ngo4444/fingerprint_esp32}

\end{document}